% populate from https://www.halfwaytothefuture.org/programme?preview=true&showLatex=true


\day{Unscheduled sessions}
\begin{sessions}
\session{Unsched.}{Ubiquitous Computing panel} \\
    \event{Keynote%
}%
    {Moving on from Weiser’s Vision of Calm Computing: Engaging UbiComp Experiences%
}%
    [Yvonne Rogers (UCL)%
]%
    {Yvonne will give the keynote for the Ubiquitous Computing session, reflecting upon her highly influential paper Moving on from Weiser’s Vision of Calm Computing: Engaging UbiComp Experiences.
More details about this keynote will be published closer to the time.%
}
\session{Unsched.}{Mixed Reality panel} \\
    \event{Keynote%
}%
    {Orchestrating a Mixed Reality Performance%
}%
    [Steve Benford (University of Nottingham)%
]%
    {Steve will give the keynote for the Mixed Reality session, reflecting upon the Desert Rain collaboration with Blast Theory, documented in Koleva et al.'s highly inflential paper Orchestrating a Mixed Reality Performance.
More details about this keynote will be published closer to the time.%
}
\session{Unsched.}{Arts \& Design-led Approaches panel} \\
    \event{Keynote%
}%
    {Ambiguity as a Resource for Design%
}%
    [Bill Gaver (Goldsmiths, University of London)%
]%
    {Bill will give the keynote for the Arts \&amp; Design-led Approaches session, reflecting upon his highly influential paper Ambiguity as a Resource for Design.
More details about this keynote will be published closer to the time.%
}
\session{Unsched.}{Public \& Private Spaces panel} \\
    \event{Keynote%
}%
    {Collaboration and Control: Crisis Management and Multimedia Technology in London Underground Line Control Rooms%
}%
    [Christian Heath and Paul Luff (King's College London)%
]%
    {Christian and Paul will give the keynote for the Public \&amp; Private Spaces session, reflecting upon their highly influential paper Collaboration and Control: Crisis Management and Multimedia Technology in London Underground Line Control Rooms.
More details about this keynote will be published closer to the time.%
}
\session{Unsched.}{New Approaches to Research \& Design panel} \\
    \event{Keynote%
}%
    {When second wave HCI meets third wave challenges%
}%
    [Susanne Bødker (Aarhus University)%
]%
    {Susanne will give the keynote for the New Approaches to Research \&amp; Design session, reflecting upon her highly influential paper When second wave HCI meets third wave challenges.
More details about this keynote will be published closer to the time.%
}
\end{sessions}

\day{Monday 18th November}
\begin{sessions}
\session{19:00}{Welcome reception} \\
\end{sessions}

\day{Tuesday 19th November}
\begin{sessions}
\session{08:00}{Registration} \\
\session{09:00}{Welcome and opening address} \\
\session{15:30}{Artificial Intelligence, Humans \& Machines panel} \\
    \event{Keynote%
}%
    {Human-Machine Reconfigurations: Plans and Situated Actions%
}%
    [Lucy Suchman (Lancaster University) and Alex Taylor (City, University of London)%
]%
    {Lucy (attending via video link) will have a conversation with Alex as part of the keynote for the Artificial Intelligence, Humans \&amp; Machines session, reflecting upon Lucy's highly influential book Human-Machine Reconfigurations: Plans and Situated Actions.
More details about this keynote will be published closer to the time.%
}
\session{17:30}{Drinks reception} \\
\session{19:00}{Symposium dinner} \\
\end{sessions}
